OSF management

### 2022-06-15 scripts/r/00-manage-osf.Rmd
♻️ - move osf files to data and scripts

```{r knit-readmes, message=FALSE, warning=FALSE}
readme_rmds <- list.files("./osf/data", pattern = "[.]Rmd$", recursive = T, full.names = T)

@@

write_csv(ratings, "./osf/data/norming/ratings/ratings.csv")

@@

write_csv(ratings_summary, "./osf/data/norming/ratings/ratings_summary.csv")
```

@@

  write_csv(tbl, file = paste0("./osf/data/production/trial-lists/", speaker, ".csv"))
}
```

@@

```{r upload-files, eval=FALSE}
osf_upload(osf_data, path = "./osf/data/norming", recurse = T, verbose = T)
osf_upload(osf_data, path = "./osf/data/production", recurse = T, verbose = T)
osf_upload(osf_data, path = "./osf/data/README.md", recurse = T, verbose = T)
osf_upload(osf_data, path = "./osf/data/methods_norm_prod.pdf", recurse = T, verbose = T)
```

>>>>

```{r knit-readmes, message=FALSE, warning=FALSE}
readme_rmds <- list.files("./data/osf", pattern = "[.]Rmd$", recursive = T, full.names = T)

@@

write_csv(ratings, "./data/osf/norming/ratings/ratings.csv")

@@

write_csv(ratings_summary, "./data/osf/norming/ratings/ratings_summary.csv")
```

@@

  write_csv(tbl, file = paste0("./data/osf/production/trial-lists/", speaker, ".csv"))
}
```

@@

```{r upload-files, eval=FALSE}
osf_upload(osf_data, path = "./data/osf/norming", recurse = T, verbose = T)
osf_upload(osf_data, path = "./data/osf/production", recurse = T, verbose = T)
osf_upload(osf_data, path = "./data/osf/README.md", recurse = T, verbose = T)
osf_upload(osf_data, path = "./data/osf/methods_norm_prod.pdf", recurse = T, verbose = T)
```
